Equilibria and Convergence of Fictitious Play\\ on Network Aggregative Games

### 2021-05-28 Documents/FP in NAGs/neurips_2021.tex
various edits

\title{Equilibria and Convergence of Fictitious Play on Network Aggregative Games}

@@

\author{%
 Aamal Hussain  \\
  Department of Computing\\
  Imperial College London\\
  South Kensington, London \\
  \texttt{aamal.hussain15@imperial.ac.uk} \\
  % examples of more authors
  \And
  Francesco Belardinelli
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
Understanding the long term behaviour of learning algorithms is an important object of study if we are to design systems which can be considered safe.In this study, we contribute towards the study of learning with multiple agents. We do this through the introduction of learning on Network Aggregative games, in which each player's reward depends only on its own strategy and a convex combination of its neighbours. In particular, we present a continuous time analysis of the Fictitious Play learning dynamic on such a game. We show that Fictitious Play reaches a fixed point when the game is zero-sum and provide conditions under which this fixed point corresponds to a Nash Equilibrium. In addition, we show that agents learning through Fictitious Play achieve no-regret, regardless of the choice of game. Finally, we present experimental evidence of a family of games for which Fictitious Play reaches a limit cycle and evidence that the introduction of noise has the potential to break this cyclic behaviour and allow agents to reach the Nash Equilibrium.
\end{abstract}

@@

Multi-Agent Learning \cite{Schwartz2014} requires a number of agents to adapt in an environment where
each agent responds to the behaviour of the other agents. This leads to a
fundamentally non-stationary problem, which presents a challenge to designing effective learning
policies. Even when there are a small number of agents in the game, learning has been shown to lead
to non-stationary, and even chaotic behaviour \cite{Sato2002}, a problem which becomes even more
pronounced as the number of agents increase \cite{Sanders2018}. In this light, it would seem that, when there is a large population of agents, it is almost difficult to understand the long term behaviour of multi-agent learning \cite{Chotibut2021}. This, of course, poses a problem for AI safety, for which it is desirable that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.

To deal with this problem, one must attempt to reduce the many player game to something which is
tractable. A number of reductions have been proposed, most notably \emph{Mean Field} Games
and \emph{Aggregative} Games. The former makes the assumption of an infinite
number of agents, so that the population can be represented through a distribution over players'
states \cite{Huang2006}. Every agent then updates their action profiles depending on this
distribution. In the latter each agent considers a real valued function which is a convex
combination of the states of the other agents. Both formulation allows for a many player game to be reduced to a set of two-player games.

Both formulations have been the object of rigorous study and it has been shown that agents reach an equilibrium when learning on such games (c.f. \cite{Perrin2020} for Mean Field Games and
\cite{Jensen2010, DePersis2020, Parise2020} for Aggregative Games). However, both also present a fundamental limitation.
Namely, they both require that agents have access to the action profiles of the entire population.
This could be through communication with all other agents, or through the intervention of a central
coordinator who is able view the entire population. Whilst recent work aims to relax this assumption
through the introduction of noise \cite{Perrin2020} or partial observability \cite{Elie2020}, the
requirement that each agent updates their actions based on the entire population is rather strong and not always supported by empirical evidence.

In this study, we investigate a variant of the aggregative game known as the \emph{Network
Aggregative} (NA) Game. This format assumes that each agent updates their actions according only to those agents with whom they are connected on an underlying network. This significantly relaxes the communication load on each agent and
lifts the need for a central coordinator. Recent work on NA games has shown that it is possible
for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Koshal2016, Shokri2020, Shokri2021, Parise2015}. We contribute in this direction by analysing the long term behaviour of learning on an NA game. In particular, we analyse the Fictitious Play Learning
Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely to the past behaviour of the others.

\paragraph{Contributions.}
%
  The main contribution of this work is to introduce and study learning on the Network Aggregative Game
  through the action of Fictitious Play (FP). In particular, we aim to establish guarantees of convergence for learning under certain classes of games. This allows for games to be designed so that the long term behaviour of learning is predictable, regardless of how many agents are engaged in the game. As such, we are able to avoid the pitfalls of chaotic dynamics in games with many players as in \cite{Sanders2018}.

  We first show that, in aggregative games played with FP, a Nash Equilibrium exists and that FP admits
  solutions in this setting. In particular, we study zero-sum games and show that
  FP converges to a fixed point which, for a network without any
  self-loops (i.e. agents are not `connected' to themselves), corresponds to a Nash Equilibrium. In addition, we find that, for games
  which are not zero-sum, agents following FP are able to
  achieve no regret.

  Finally, we explore FP through numerical simulations to consider the
  question of whether it always converges. We answer this in the negative by finding a family of
  games in which action profiles cycle around the Nash Equilibrium. Finally, our experiments
  document how noise affects the convergence of FP. Our experiments suggest that, under
  the presence of noise, the algorithm still reaches a fixed point, but perhaps not the Nash
  Equilibrium. This presents an interesting avenue for future research.

  To the best of our knowledge, this paper is the first time that a learning algorithm, which stems from game theoretic literature, has been studied on the Network Aggregative game, typically considered in the context of control and optimisation.

@@

\textbf{Network Aggregative Games}
%NA games
are a recent introduction \cite{Parise2015} which presents
a variant of aggregative games by adding an underlying structure to
the population. Since its introduction, distributed algorithms have
been built with the aim of finding NE. In particular,
\cite{Parise2015, Parise2020} consider the case in which payoffs are
given by Lipschitz functions with unique minimisers and apply standard
topological fixed point arguments towards designing algorithms which will
converge to the NE. Another approach for distributed NE seeking is the
projected gradient (resp. subgradient) dynamics which is explored in
\cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these
works, the cost function is assumed to be convex, and therefore have a
unique minimiser. In fact this is a common assumption in works
concerning NA Games \cite{Zhu2021, Lei2020} which, we believe, is due
to its ubiquity in control settings. We have not yet come across works
which consider NA games from the point of view of payoff matrices,
which are more common in multi-agent learning settings.  Furthermore,
to the best of our knowledge, this is the first work which introduces
the application of a learning algorithm in the NA setting.

\textbf{Fictitious Play}

was introduced in 1951 \cite{Brown1949} as a `natural'
way in which to approximate the Nash Equilibrium in zero-sum games. Since then, a number of proofs of convergence have been determined for 2 player games \cite{Robinson1951, Miyasawa1961, Metrick1994,Berger2007, Monderer1997, Monderer1996}. However, the work looking
at FP where there are more than two agents is sparse. \cite{Sela1999}
considers a game in which a multi-player game is decomposed by
requiring that each agent engage in a two person game against each of
the opponent. Their payoff is given by the sum of payoffs in all of
these subgames. It was found that, if this game is zero-sum, then FP
will converge. Similar results for more than two players were found
for games where all agents share the same payoff in
\cite{Monderer1996}. In \cite{Perrin2020}, the action of FP was
considered in a Mean Field Game, with convergence in zero-sum
games. The most general result, and the one most similar to our own,
was found by Ewerhart and Valkanova in 2020 \cite{Ewerhart2020}. It was found that FP converges in network games, where each
agent is engaged in a two-player game with each of their neighbours
Our work adapts this model to consider NA Games, so that the agents do not play
individual games against each of their neighbours but rather a single
game against the aggregate of their neighbours. We also
go beyond the zero-sum requirement by exteding a result for two player games found in
\cite{Ostrovski2014} which showed that FP achieves no-regret to the
multi-player setting.

>>>>

\title{Equilibria and Convergence of Fictitious Play\\ on Network Aggregative Games}

@@

%\author{%
% Aamal Hussain  \\
%  Department of Computing\\
%  Imperial College London\\
%  South Kensington, London \\
%  \texttt{aamal.hussain15@imperial.ac.uk} \\
  % examples of more authors
%  \And
%  Francesco Belardinelli
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
%}

@@

\begin{abstract}
Understanding the long term behaviour of learning algorithms is an
important object of study if we are to design AI systems that are
%can be considered
safe. In this work, we contribute towards the study of
learning with multiple agents. We do this through the introduction of
learning on Network Aggregative (NA) games, in which each player's reward
depends only on its own strategy and a convex combination of its
neighbours. In particular, we present a continuous time analysis of
the Fictitious Play learning dynamic on NA games. We show that
Fictitious Play reaches a fixed point when the game is zero-sum, and
provide conditions under which this fixed point corresponds to a Nash
equilibrium. In addition, we show that agents learning through
Fictitious Play achieve no-regret, regardless of the choice of
game. Finally, we present experimental evidence of a family of games
for which Fictitious Play reaches a limit cycle and evidence that the
introduction of noise has the potential to break this cyclic behaviour
and allow agents to reach the Nash equilibrium.
\end{abstract}

@@

Multi-agent learning \cite{Schwartz2014} requires a number of agents
to adapt in an environment, where each agent responds to the behaviour
of the other agents. This feature leads to a fundamentally non-stationary
problem, which presents a challenge to designing effective learning
policies. Even for a small number of agents in the game,
learning has been shown to lead to non-stationary, and even chaotic
behaviour \cite{Sato2002}, a problem that becomes even more
pronounced as the number of agents increases \cite{Sanders2018}. In
this light, it would seem that, when there is a large population of
agents, it is extremely difficult to understand the long-term behaviour
of multi-agent learning \cite{Chotibut2021}. This difficulty, of course, poses a
problem for AI safety, for which it is desirable that learning systems
are designed so that their ultimate behaviour is guaranteed to satisfy
some predetermined goals.

To solve this problem, a promising approach is to reduce the
many-player game to something that is tractable. A number of
reductions have been proposed, most notably \emph{Mean Field} games
and \emph{Aggregative} games. The former make the assumption of an
infinite number of agents, so that the population can be represented
through a distribution over players' states \cite{Huang2006}. Every
agent then updates their action profiles depending on this
distribution. In the latter, each agent considers a real valued
function which is a convex combination of the states of the other
agents. Both approaches allow for a many-player game to be reduced
to a set of two-player games.
%
Further, both approaches have been the object of rigorous study, which has
 shown that agents reach an equilibrium when learning on such
games (cf.~\cite{Perrin2020} for Mean Field Games and
\cite{Jensen2010, DePersis2020, Parise2020} for Aggregative
Games). However, both also present a fundamental limitation.  Namely,
they both require that agents have access to the action profiles of
the entire population.  This could be through communication with all
other agents, or through the intervention of a central coordinator who
is able access the entire population. Whilst recent work aims to relax
this assumption through the introduction of noise \cite{Perrin2020} or
partial observability \cite{Elie2020}, the requirement that each agent
updates their actions based on the entire population is rather strong
and not always supported by empirical evidence.

In this study, we investigate a variant of aggregative games:
%known as the
\emph{Network Aggregative} (NA) games. This framework assumes that
each agent updates their actions according only to those agents with
whom they are connected on an underlying network. This assumption
significantly relaxes the communication load on each agent and lifts
the need for a central coordinator. Recent work on NA games has shown
that it is possible for agents to reach an equilibrium strategy in an
entirely distributed manner \cite{Koshal2016, Shokri2020, Shokri2021,
  Parise2015}. We contribute in this direction by analysing the
long-term behaviour of multi-agent learning on NA games. In
particular, we analyse the Fictitious Play learning algorithm
\cite{Brown1949,Harris1998}, in which agents are assumed to be
myopic, in that they react solely to the past behaviour of the others.

\paragraph{Contributions.}
%
  The main contribution of this work is to introduce and study convergence of
  learning on Network Aggregative games through the action of
  Fictitious Play (FP). In particular, we aim to establish guarantees
  of convergence for learning under certain classes of games. Such guarantees
  allow for games to be designed so that the long-term behaviour of
  learning is predictable, regardless of how many agents are engaged
  in the game. As such, we are able to avoid the pitfalls of chaotic
  dynamics in games with many players, as shownin \cite{Sanders2018}.

  We first show that, in NA games played with FP, a Nash equilibrium
  exists and that FP admits solutions in this setting. Specifically,
  we study zero-sum games and show that FP converges to a fixed point
  which, for a network without any self-loops (i.e., agents are not
  `connected' to themselves), corresponds to a Nash equilibrium. In
  addition, we find that, for games which are not zero-sum, agents
  following FP are able to achieve no regret.

  Further, we explore FP through numerical simulations to check
  %consider the
  %question of
  whether it always converges. We answer this question
  negatively, by finding a family of games in which action profiles cycle
  around the Nash equilibrium. Finally, our experiments document how
  noise affects the convergence of FP, suggesting that,
  under the presence of noise, the algorithm still reaches a fixed
  point, but perhaps not the Nash equilibrium. This presents an
  interesting avenue for future research.

  To the best of our knowledge, this contribution is the first time that a
  learning algorithm, which stems from game-theoretic literature, has
  been studied on Network Aggregative games, typically considered
  in the context of control and optimisation.

@@

\textbf{Network Aggregative Games}
%NA games
are a recent extension \cite{Parise2015}
%which presents a variant of
of aggregative games, obtained by adding an underlying structure to
the population. Since its introduction, distributed algorithms have
been built with the aim of finding NE in NA games. In particular,
\cite{Parise2015, Parise2020} consider the case in which payoffs are
given by Lipschitz functions with unique minimisers and apply standard
topological fixed-point arguments towards designing algorithms that
converge to the NE. Another approach for searching for distributed NE the
projected gradient (resp. subgradient) dynamics, which is explored in
\cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all these
works, the cost function is assumed to be convex, and therefore has a
unique minimiser. In fact, this is a common assumption in works
about NA games \cite{Zhu2021, Lei2020} which, we believe, is due
to its ubiquity in control settings. We have not yet come across works
which consider NA games from the point of view of payoff matrices,
which are more common in multi-agent learning settings.  Furthermore,
to the best of our knowledge, this is the first work which introduces
the application of a learning algorithm in NA games.

\textbf{Fictitious Play} was introduced
%in 1951
as a `natural' way to approximate Nash equilibria in zero-sum games
\cite{Brown1949}. Since then, a number of results on convergence have
been proved for two-player games \cite{Robinson1951, Miyasawa1961,
  Metrick1994,Berger2007, Monderer1997, Monderer1996}. However, 
works looking at FP with more than two agents is
sparse. In \cite{Sela1999}
%considers
%a game in which a
multi-player games
are decomposed
%by requiring that each agent engage
in two-plpayer games between each pair of players in the game.
%against each of the opponent.
Each agent's payoff is given by the sum of
payoffs in all of these subgames. It was found that, if this game is
zero-sum, then FP converges. Similar results for more than two
players were found for games where all agents share the same payoff in
\cite{Monderer1996}. In \cite{Perrin2020}, the action of FP was
considered in a Mean Field game, with convergence in zero-sum
games. The most general result, and the one most similar to our own,
appears in
%was found by Ewerhart and Valkanova in 2020
\cite{Ewerhart2020}, in which the authors show
%. It
%was found
that FP converges in network games, where each agent is
engaged in a two-player game with each of their neighbours
Our work extends the analysis
of FP in multi-player games by considering its action in NA games,
%Our work
%adapts this model to consider NA Games,
so that the agents do not play
individual games against each of their neighbours, but rather a single
game against the aggregate of their neighbours. We also go beyond the
zero-sum requirement by exteding a result for two-player games
in \cite{Ostrovski2014} which showed that FP achieves no-regret in the
multi-player setting.
